---
title: "What the MATH4753AminatO package does - Oyeleke Aminat"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{What the package does}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753AminatO)
```


# Introduction

This package is basically a summary of the functions that I considered more interesting or useful during my learning, all of them are
taken from the laboratories we have done in the course so far.

# R functions

## mybin.R

This function performs a binomial simulation, it has default values of iter=100, p=0.5, and n=10.It returns a barplot of relative frequencies and a table of the same


```{r}
mybin()
```

## myboot.R

This is a function created to run the bootstrap simulation technique to estimate a confidence interval of a parameter of interest.

```{r}
s=c(3,4,5,6)
myboot(x=s)
```



## myconfint.R


This is a more basic function, this is an example of how R can be used as a calculator, to estimate the interval of the mean of a single sample.

```{r}
myci(c(3,4,5,6))
```

## myncurve.R

This function creates a normal distribution curve using the mean and the standard deviation as varaiables, and also estimates the lower tail probability (1- alpha) of a point of interest. 
```{r}
myncurve(mu=10,sigma=2,p=9)
```
